Reduced Nucleotide Diversity on a Plant Y Chromosome Following Recent Recombination Suppression

### 2016-08-02 manuscript.tex
minor edits

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{Figure1.png}
\caption{The relation between relative effective population size and sex ratio bias for genes on autosomes (\textbf{A}) and sex chromosomes (\textbf{B}; Y chromosome in red). The sex ratio is shown as the proportion of males, $N_{m}/(N_{f}+N_{m})$, where $N_{m}$ and $N_{f}$ are the effective number of breeding males and females, respectively, plotted against $N_{e}/N$, where $N=N_{m}+N_{f}$. Dotted lines show predictions where both males and females produce Poisson-distributed offspring numbers. In that case, the $N_{e}$'s are given by $N_{e{A}}=4N_{m}N_{f}/(N_{m}+N_{f})$ for autosomes, $N_{e{X}}=9N_{m}N_{f}/(4N_{m}+2N_{f})$ for the X, and $N_{e{Y}}=N_{m}/2$ for the Y \citep{wright1931evolution}. The other curves correspond to increasing levels of variance in male reproductive success \citep{nomura2002effective} (see Methods). Assuming $\theta=4N_{e}\mu$ and equal neutral mutation rates among genes, the predicted $N_{e}$'s are used to generate our null expectations for the X/A and Y/A ratios of diversity.  
}%
\label{fig:spectrum}
\end{figure}

\subsection*{Simulations of Background Selection and Selective Sweeps}
To investigate whether our observed level of Y-chromosome diversity could be explained by background selection, we conducted forward time simulations.....We modeled both purifying and positive selection using the forward simulation software SFSCODE \citep{hernandez2008flexible}. To make the simulation output more comparable to our data, we used estimates of $\theta$ from our polymorphism data as a simulation input parameter, and sampled 8 Y chromosomes per simulation from 24 populations to match out empirical data. To consider the effects of selection against deleterious alleles, we sampled selective coefficients from a gamma distribution with shape parameter 0.1, mean selection coefficient $s=-0.01$, neutral mutation rate $\mu = 0.005$, deleterious mutation rate $U=0.01$ (diploid), and dominance term $h=1$. We then calculated the average $\theta$ over all simulations, and obtained the Y/A ratio of neutral diversity under the model and compared this to our empirical data (\X new figure). Confidence intervals were calculated from bootstrapping 10000 replicate simulations  using the BCa method (Efron 1987) implemented in the Boot package in R (Canty and Ripley 2012; R Core Team 2011).

\begin{equation}
S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i
\label{eq:refname1}
\end{equation}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{Figure1.png}
\caption{The relation between relative effective population size and sex ratio bias for genes on autosomes (\textbf{A}) and sex chromosomes (\textbf{B} (Y chromosome in red). The sex ratio is shown as the proportion of males, $N_{m}/(N_{f}+N_{m})$, where $N_{m}$ and $N_{f}$ are the effective number of breeding males and females, respectively, plotted against $N_{e}/N$, where $N=N_{m}+N_{f}$. Dotted lines show predictions where both males and females produce Poisson-distributed offspring numbers. In that case, the $N_{e}$'s are given by $N_{e{A}}=4N_{m}N_{f}/(N_{m}+N_{f})$ for autosomes, $N_{e{X}}=9N_{m}N_{f}/(4N_{m}+2N_{f})$ for the X, and $N_{e{Y}}=N_{m}/2$ for the Y \citep{wright1931evolution}. The solid curves correspond to increasing levels of variance in male reproductive success \citep{nomura2002effective} (see Methods). Assuming $\theta=4N_{e}\mu$ and equal neutral mutation rates among genes, the predicted $N_{e}$'s are used to generate our null expectations for the X/A and Y/A ratios of diversity.  
}%
\label{fig:spectrum}
\end{figure}

\subsection*{Simulations of positive and purifying selection}
To investigate whether our observed level of Y-chromosome diversity could be explained by background selection, we conducted forward time simulations, modeling both purifying and positive selection on the Y chromosome using the software SFSCODE \citep{hernandez2008flexible}. To make the simulation output comparable to our data, we initialized simulations with an empirically estimated value of $\theta$ (from autosomes), and sampled 8 Y chromosomes per simulation from 24 populations. To consider the effects of selection against deleterious alleles (purifying selection), we sampled selective coefficients from a gamma distribution with shape parameter $k=0.1$, mean selection coefficient $s=-0.01$, neutral mutation rate $\mu = 0.005$, deleterious mutation rate $U=0.01$ (diploid). For positive selection simulations, we used \X [parameters here]. We ran 1000 replicates for each model and we calculated the average $\theta_{sim}$ over all simulation output to obtain the simulated Y/A ratio of neutral diversity under the both models (purifying and positive selection), taking into account unequal male and female population sizes. We compared simulated diversity output to our empirical data (\X new figure) by calculating the proportion of simulation replicates for which $\theta_{sim}$ was not significantly different from $\theta_{observed}$, using a two-sided P value. Commands for running the simulations are provided in the Supplementary Material.
